---
title: "Non_Household_Contacts"
author: "Christopher Soria"
date: "2023-12-02"
output: html_document
---

```{r}
library(data.table)
library(tidyverse)
library(dplyr)
library(MASS)
library(gridExtra)
library(broom)

df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
D_df <- df[df$political_party == "Democrat"]
R_df <- df[df$political_party == "Republican"]

names(df) <- make.unique(names(df))
names(RD_df) <- make.unique(names(RD_df))
names(D_df) <- make.unique(names(D_df))
names(R_df) <- make.unique(names(R_df))
```
1.6 means that Republicans are expected to have 1.6 times as many non-household contacts as Democrats, on average.

```{r}
# Model for Wave 1
contacts_R_v_D_w1 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 2))

# Model for Wave 2
contacts_R_v_D_w2 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 4))
# Model for Wave 3
contacts_R_v_D_w3 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 6))

# Define a new function to extract both the coefficient and its standard error
extract_coefficient_and_error <- function(model, coefficient_name) {
  estimate <- coef(summary(model))[coefficient_name, "Estimate"]
  std_error <- coef(summary(model))[coefficient_name, "Std. Error"]
  list(coefficient = exp(estimate), 
       lower = exp(estimate - 1.96 * std_error), 
       upper = exp(estimate + 1.96 * std_error))
}

# Extract coefficients and standard errors for each wave
coeff_wave1 <- extract_coefficient_and_error(contacts_R_v_D_w1, "political_partyRepublican")
coeff_wave2 <- extract_coefficient_and_error(contacts_R_v_D_w2, "political_partyRepublican")
coeff_wave3 <- extract_coefficient_and_error(contacts_R_v_D_w3, "political_partyRepublican")

# Combine coefficients into a data frame
coefficients_df <- data.frame(
  Wave = factor(c(1, 2, 3)),
  Coefficient = c(coeff_wave1$coefficient, coeff_wave2$coefficient, coeff_wave3$coefficient),
  Lower = c(coeff_wave1$lower, coeff_wave2$lower, coeff_wave3$lower),
  Upper = c(coeff_wave1$upper, coeff_wave2$upper, coeff_wave3$upper)
)

contacts_R_v_D_plot <- ggplot(coefficients_df, aes(x = Wave, y = Coefficient, shape = Wave)) +  # Add shape mapping to aes()
  geom_point(position = position_dodge(width = 0.25), size = 3, color = "red") +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.1, position = position_dodge(width = 0.25), color = "red") +
  scale_shape_manual(values = c(16, 15, 17),  # Define shapes for each wave
                     labels = c("Wave 1", "Wave 2", "Wave 3")) +  # Custom labels for the legend
  labs(title = "Wave-Specific Comparative Non-Household Contacts for Republicans During the Pandemic",
       subtitle = "Reference: Democrats",
       x = "Wave",
       y = "IRR",
       shape = "Wave Shapes") +  # Label for the shape legend
  theme_minimal() +
  theme(legend.position = "bottom")  # Adjust legend position

rm(coeff_wave1,coeff_wave2,coeff_wave3,contacts_R_v_D_w1,contacts_R_v_D_w2,contacts_R_v_D_w3)
# Print the plot
print(contacts_R_v_D_plot)
```
Strange and inconcistent results with Democrats in Republican CD's
Wave 2 I don't see any difference between them and D in R CD
Wave 4 I see they're MORE likely to have non-hh contacts in R CD
Wave 6 I see they're LESS likely to have non-hh contacts in R CD

However, Republicans are pretty consitently having more non-hh contacts over time (the only clear pattern)
```{r}
contacts_DC_w2 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 2))

# Model for Wave 2
contacts_DC_w4 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 4))
# Model for Wave 3
contacts_DC_w6 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 6))

# Coefficients of interest
coeffs_of_interest <- c("political_party_to_CDDemocrat in Republican led CD",
                        "political_party_to_CDRepublican in Democratic led CD",
                        "political_party_to_CDRepublican in Republican led CD")

# Apply the function to each model
coeff_wave2 <- extract_coefficient_and_error(contacts_DC_w2, coeffs_of_interest)
coeff_wave4 <- extract_coefficient_and_error(contacts_DC_w4, coeffs_of_interest)
coeff_wave6 <- extract_coefficient_and_error(contacts_DC_w6, coeffs_of_interest)

# Add wave information to each data frame
coeff_wave2$Wave <- "Wave 1"
coeff_wave4$Wave <- "Wave 2"
coeff_wave6$Wave <- "Wave 3"

term_names_wave2 <- names(coeff_wave2$coefficient)
term_names_wave4 <- names(coeff_wave4$coefficient)
term_names_wave6 <- names(coeff_wave6$coefficient)

# Combine coefficients into a data frame
coefficients_df <- data.frame(
  Wave = factor(c(1, 1, 1, 2, 2, 2, 3, 3, 3)),
  Coefficient = c(coeff_wave2$coefficient, coeff_wave4$coefficient, coeff_wave6$coefficient),
  Lower = c(coeff_wave2$lower, coeff_wave4$lower, coeff_wave6$lower),
  Upper = c(coeff_wave2$upper, coeff_wave4$upper, coeff_wave6$upper),
  Term = c(term_names_wave2, term_names_wave4, term_names_wave6)
)

contacts_DC_plot <- ggplot(coefficients_df, aes(x = Term, y = Coefficient, color = Term, shape = Wave)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +  # Dodge applied to points
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.1, position = position_dodge(width = 0.3)) +  # Dodge also applied to error bars
  scale_color_manual(name = "Term", 
                     values = c("blue", "purple", "red"),
                     labels = c("Dem in Rep CD", "Rep in Dem CD", "Rep in Rep CD")) +
  scale_shape_manual(values = c(16, 15, 17)) +
  theme_minimal() +
  labs(title = "Wave-Specific Comparative Non-Household Contacts for Partisans Within Congressional District Context", 
       subtitle = "Reference: Dems in Dem Districts",
       x = "Category", 
       y = "IRR") +
  scale_x_discrete(labels = c("Dems in Repub Disctricts", "Repubs in Dem Districts", "Repubs in Repub Distritics")) # Custom x-axis labels

print(contacts_DC_plot)
```

