---
title: "Opposing Party CD"
author: "Christopher Soria"
date: "2023-11-04"
output: html_document
---
```{r}
library(data.table)
library(tidyverse)
library(dplyr)
library(patchwork)
```

```{r}
df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
```


Being in an opposing party CD means less likely to say there was a reduction in contact
I decided to control for whether the person is an Independent, but maybe that doesn't make sense?
```{r}
opp_contact_reduction_model <- glm(contact_reduction ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD + Independent, data = df, family = binomial)

tidy_model <- broom::tidy(opp_contact_reduction_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("In_Opposing_Party_CD")) %>%
  mutate(odds_ratio = exp(estimate),
         term = recode(term, 
                       In_Opposing_Party_CD = ""))

# Plot
opp_contact_reduction_plot <- ggplot(coeffs_of_interest, aes(x = term, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = c("Orange"), width = 0.7) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +  # Set the upper limit to 1
  labs(y = "Odds Ratio", x = "Opposite-Party-Dominant ZIP Code", 
       title = "Likelihood of Reduced Contact Due to COVID-19 by Partisan ZIP Code Majority",
       subtitle = "Reference: Same-Party-Dominant ZIP Code") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(opp_contact_reduction_plot)

# View the model summary
summary(opp_contact_reduction_model)
rm(opp_contact_reduction_model)
```
Being in an opposing party CD means less likely to be concerened about the spread of the virus
```{r}
opp_concern_model <- glm(binary_concern_strong ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD, data = df, family = binomial)

# View the model summary
tidy_model <- broom::tidy(opp_concern_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("In_Opposing_Party_CD")) %>%
  mutate(odds_ratio = exp(estimate),
         term = recode(term, 
                       In_Opposing_Party_CD = ""))

# Plot
opp_concern_plot <- ggplot(coeffs_of_interest, aes(x = term, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = c("Orange"), width = 0.7) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +  # Set the upper limit to 1
  labs(y = "Odds Ratio", x = "Opposite-Party-Dominant ZIP Code", 
       title = "Likelihood of Concern of Spread of COVID-19 by Partisan ZIP Code Majority",
       subtitle = "Reference: Same-Party-Dominant ZIP Code") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

combined_opp_plot <- opp_concern_plot + opp_contact_reduction_plot + plot_layout(ncol = 2)
print(combined_opp_plot)

summary(opp_concern_model)
rm(opp_concern_model)
```
However, being in an opposing CD doesn't really change the outcome of how many people you're likely to interact with in the previous day
```{r}
opp_contact_model <- lm(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD + Independent, data = df)

# View the model summary
summary(opp_contact_model)
rm(opp_contact_model)
```
being in an opposing cd means you're less likely to wear masks, unless I control for Independent
Meaning that being in opposing CD means you're less likely to wear masks only because Independents are less likely to wear masks
And Independents are more often in the category of "in opposing CD"
```{r}
opp_masked_contact_model <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD, data = df)

opp_masked_contact_model2 <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD + Independent, data = df)

# View the model summary
summary(opp_masked_contact_model)
summary(opp_masked_contact_model2)
rm(opp_masked_contact_model)
rm(opp_masked_contact_model2)
```
Overall, they're less likely to be safe in their contacts
But only by .01 (not much of a difference)
```{r}
opp_safety_model <- lm(Non_Weighted_Safety_Index ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD + Independent, data = df)

# View the model summary
summary(opp_safety_model)
rm(opp_safety_model)
```
However, despite republicans and democrats not being more or less likely to get vaccinated
being in an opposite party means you're less likely to get vaccinated
```{r}
opp_vax_model <- glm(Vaccinated ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + In_Opposing_Party_CD + Independent, data = df, family = binomial)

# View the model summary
tidy_model <- broom::tidy(opp_vax_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("In_Opposing_Party_CD")) %>%
  mutate(odds_ratio = exp(estimate),
         term = recode(term, 
                       In_Opposing_Party_CD = ""))

# Plot
opp_vax_plot <- ggplot(coeffs_of_interest, aes(x = term, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = c("Orange"), width = 0.7) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +  # Set the upper limit to 1
  labs(y = "Odds Ratio", x = "Opposite-Party-Dominant ZIP Code", 
       title = "Likelihood of Vaccination in mid 2021 by Partisan ZIP Code Majority",
       subtitle = "Reference: Same-Party-Dominant ZIP Code") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# View the model summary
summary(opp_vax_model)

opp_vax_plot

rm(opp_vax_model)
```

