---
title: "Republicans in Democratic CDs"
author: "Christopher Soria"
date: "2023-11-04"
output: html_document
---
```{r}
library(data.table)
library(tidyverse)
library(dplyr)
```

```{r}
df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
```


The closer to republicanisn the less contact reduction
```{r}
dvr_contact_reduction_model <- glm(contact_reduction ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# View the model summary
summary(dvr_contact_reduction_model)
rm(dvr_contact_reduction_model)
```
Republicans generally are less concerned than democrats
```{r}
dvr_concern_model <- glm(binary_concern_strong ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# View the model summary
summary(dvr_concern_model)
rm(dvr_concern_model)
```
However, being in an opposing CD doesn't mean you're less likely to report contact
Independents are having the most contact
Democrats are not more or less likely to have contact with people in different settings
```{r}
dvr_contact_model <- lm(Contacts ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# View the model summary
summary(dvr_contact_model)
rm(dvr_contact_model)
```
Democrats are less likely to wear masks when they're in Republican districts
Republicans are more likely to wear masks when they're in Democratic districts
Suggesting some peer pressure effects based on majority
```{r}
dvr_masked_contact_model <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# View the model summary
summary(dvr_masked_contact_model)
rm(dvr_masked_contact_model)
```
Overall, they're less likely to be safe in their contacts
```{r}
dvr_safety_model <- lm(Non_Weighted_Safety_Index ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# View the model summary
summary(dvr_safety_model)
rm(dvr_safety_model)
```

```{r}
dvr_vax_model <- glm(as.factor(covid19_vax) ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# View the model summary
summary(dvr_vax_model)
rm(dvr_vax_model)
```

