---
title: "Republicans versus Democrats"
author: "Christopher Soria"
date: "2023-11-04"
output: html_document
---
```{r}
library(data.table)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(purrr)
library(broom)
library(cowplot)
```

```{r}
df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
D_df <- df[df$political_party == "Democrat"]
R_df <- df[df$political_party == "Republican"]

names(df) <- make.unique(names(df))
names(RD_df) <- make.unique(names(RD_df))
names(D_df) <- make.unique(names(D_df))
names(R_df) <- make.unique(names(R_df))
```

Republicans are less likely to reduce contact, according to what they say
```{r}
rvd_contact_reduction_model <- glm(contact_reduction ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df, family = binomial)

# View the model summary
summary(rvd_contact_reduction_model)

tidy_model <- broom::tidy(rvd_contact_reduction_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("political_partyIndependent", "political_partyRepublican")) %>%
  mutate(odds_ratio = exp(estimate),
         term = recode(term, 
                       political_partyIndependent = "Independent", 
                       political_partyRepublican = "Republican"))

# Plot
rvd_contact_reduction_plot <- ggplot(coeffs_of_interest, aes(x = term, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = c("Purple", "Red"), width = 0.7) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +  # Set the upper limit to 1
  labs(y = "Odds Ratio", x = "Political Affiliation of Person", 
       title = "Relative Odds of Saying You Have Greatly Reduced Contact As a Result of COVID-19",
       subtitle = "Reference: Democrats") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

rvd_contact_reduction_plot

rm(rvd_contact_reduction_model)
```
What about over time?
This way of presenting is not as helpful
Let's try plotting Republican over time
```{r}
create_plot <- function(data_subset) {
  model <- glm(contact_reduction ~ COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, 
               data = data_subset, family = binomial)

  results <- broom::tidy(model) %>%
    filter(term %in% c("political_partyIndependent", "political_partyRepublican")) %>%
    mutate(
      odds_ratio = exp(estimate),
      term = recode(term, 
                    political_partyIndependent = "Independent", 
                    political_partyRepublican = "Republican")
    )

  ggplot(results, aes(x = term, y = odds_ratio, color = term)) +
    geom_point(position = position_dodge(width = 0.5)) +
    geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                      ymax = exp(estimate + std.error*1.96)), position = position_dodge(width = 0.5), width = 0.2) +
    scale_y_continuous(labels = scales::comma, 
                       breaks = scales::pretty_breaks(),
                       limits = c(NA, 1)) + 
    labs(y = "Odds Ratio", x = "Political Affiliation of Person", 
         title = paste("Wave", unique(data_subset$wave), ": Odds Ratios of Reporting Reduction in Contact"),
         subtitle = "Reference: Democrats") +
    theme_minimal()
}

# Apply the function to each subset of data by wave and store plots in a list
plots <- df %>% 
  split(.$wave) %>% 
  map(~create_plot(.))

# Combine the separate plots into one
combined_plot <- cowplot::plot_grid(plotlist = plots, align = 'h')

# Print the combined plot
print(combined_plot)
```
Not much change over time in terms of how much contact reduction is stated by Republicans in comparison to Democrats
No clear trend
```{r}
results <- df %>% 
  group_by(wave) %>% 
  do({
    model <- glm(contact_reduction ~ COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = ., family = binomial)
    broom::tidy(model)
  }) %>%
  filter(term %in% c("political_partyRepublican")) %>%
  mutate(
    odds_ratio = exp(estimate),
    term = recode(term, 
                  political_partyRepublican = "Republican")
  )

# Plot for each wave
ggplot(results, aes(x = term, y = odds_ratio, group = wave, shape = as.factor(wave))) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), position = position_dodge(width = 0.5), width = 0.2) +
  scale_shape_manual(values = c(16, 17, 18)) +  # Choose your shapes here
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) + 
  labs(y = "Odds Ratio", x = "Political Affiliation of Person", 
       title = "Relative Odds of Saying You Have Greatly Reduced Contact As a Result of COVID-19 by Wave",
       subtitle = "Reference: Democrats") +
  theme_minimal()
```


Republicans are less concerned about the spread of the virus
```{r}
rvd_concern_model <- glm(binary_concern_strong ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df, family = binomial)

# View the model summary
summary(rvd_concern_model)

tidy_model <- broom::tidy(rvd_concern_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("political_partyIndependent", "political_partyRepublican")) %>%
  mutate(odds_ratio = exp(estimate),
         term = recode(term, 
                       political_partyIndependent = "Independent", 
                       political_partyRepublican = "Republican"))

# Plot
rvd_concern_plot <- ggplot(coeffs_of_interest, aes(x = term, y = odds_ratio)) +
  geom_bar(stat = "identity", fill = c("Purple", "Red"), width = 0.7) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +  # Set the upper limit to 1
  labs(y = "Odds Ratio", x = "Political Affiliation of Person", 
       title = "Relative Odds of a Person Saying They're 'Very Concerned' About the Spread of Coronavirus",
       subtitle = "Reference: Democrats") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(rvd_concern_plot)

rm(rvd_concern_model)
```
What about over time?
Hardly any change from Republicans
```{r}
results <- df %>% 
  group_by(wave) %>% 
  do({
    model <- glm(binary_concern_strong ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df, family = binomial)
    broom::tidy(model)
  }) %>%
  filter(term %in% c("political_partyRepublican")) %>%
  mutate(
    odds_ratio = exp(estimate),
    term = recode(term, 
                  political_partyRepublican = "Republican")
  )

# Plot for each wave
ggplot(results, aes(x = term, y = odds_ratio, group = wave, shape = as.factor(wave))) +
  geom_point(position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), position = position_dodge(width = 0.5), width = 0.2) +
  scale_shape_manual(values = c(16, 17, 18)) +  # Choose your shapes here
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) + 
  labs(y = "Odds Ratio", x = "Political Affiliation of Person", 
       title = "Relative Odds of Saying You Have Greatly Reduced Contact As a Result of COVID-19 by Wave",
       subtitle = "Reference: Democrats") +
  theme_minimal()
```

And Republicans also reported 1.2 more contacts on average when asked "How many people who do not live in your household did you have in-person contact with yesterday?"
```{r}
rvd_contact_model <- lm(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df)

# View the model summary
summary(rvd_contact_model)

tidy_model <- broom::tidy(rvd_contact_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("political_partyIndependent", "political_partyRepublican")) %>%
  mutate(term = recode(term, 
                       political_partyIndependent = "Independent", 
                       political_partyRepublican = "Republican"))

# Plot
rvd_contact_plot <- ggplot(coeffs_of_interest, aes(y = term, x = estimate)) +
  geom_bar(stat = "identity", fill = c("Purple", "Red"), width = 0.7, orientation = "y") +
  geom_errorbar(aes(xmin = estimate - std.error*1.96, 
                    xmax = estimate + std.error*1.96), width = 0.3, orientation = "y") +
  scale_x_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks()) +
  labs(x = "Non-Household Contacts", y = "Political Affiliation of Person", 
       title = "Relative Number of Reported Non-Household Contacts in the Previous Day",
       subtitle = "Reference: Democrats") +
  theme_minimal() +
  theme(axis.text.y = element_text(angle = 45, hjust = 1))

print(rvd_contact_plot)

rm(rvd_contact_model)
```
Republicans are less likely to wear masks
```{r}
rvd_masked_contact_model <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df)

# View the model summary
summary(rvd_masked_contact_model)

tidy_model <- broom::tidy(rvd_masked_contact_model)

coeffs_of_interest <- tidy_model %>% 
  filter(term %in% c("political_partyIndependent", "political_partyRepublican")) %>%
  mutate(term = recode(term, 
                       political_partyIndependent = "Independent", 
                       political_partyRepublican = "Republican"))

# Plot
rvd_masked_contact_plot <- ggplot(coeffs_of_interest, aes(x = term, y = estimate)) +
  geom_bar(stat = "identity", fill = c("Purple", "Red"), width = 0.7) +
  geom_errorbar(aes(ymin = estimate - std.error*1.96, 
                    ymax = estimate + std.error*1.96), width = 0.3) +
  scale_y_continuous(labels = scales::comma, 
                     breaks = scales::pretty_breaks()) +
  labs(y = "Non-Household Contacts", x = "Political Affiliation of Person", 
       title = "Relative Difference in Fraction of Contacts Carried Out With a Mask",
       subtitle = "Reference: Democrats") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(rvd_masked_contact_plot)

rm(rvd_masked_contact_model)
```
Overall, Republicans are less safe in their contacts
```{r}
rvd_safety_model <- lm(Non_Weighted_Safety_Index ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df)

# View the model summary
summary(rvd_safety_model)
rm(rvd_safety_model)
```
Democrats and republicans are not more or less likely to get the vaccine at this stage in the pandemic (mid 2021)
(TRUMP championed the vaccine)
```{r}
rvd_vax_model <- glm(as.factor(covid19_vax) ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = df, family = binomial)

# View the model summary
summary(rvd_vax_model)
rm(rvd_vax_model)
```
