---
title: "Republicans in Democratic CDs"
author: "Christopher Soria"
date: "2023-11-04"
output: html_document
---
```{r}
library(data.table)
library(tidyverse)
library(dplyr)
```

```{r}
df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
names(df) <- make.unique(names(df))
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
```


The closer to republicanism the less contact reduction
How does this fit with the previous plot on opposing party generally being less likely to say they reduced contact?
Republicans are generally less concerned and also democrats in republican districts are less concerned
```{r}
dvr_contact_reduction_model <- glm(contact_reduction ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_contact_reduction_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_contact_reduction_plot <- ggplot(selected_coeff, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.2) +
  coord_flip() +
  labs(y = "Odds Ratio", x = "", title = "Partisan Contact Reduction Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks(),
                     limits = c(NA, 1)) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red")) 

print(dvr_contact_reduction_plot)

# View the model summary
summary(dvr_contact_reduction_model)
rm(dvr_contact_reduction_model)
```
Republicans generally are less concerned than democrats
Republicans in Democratic CD's are more likely to be concerned about spread (controlling for urbanicity)
But Democrats are not more or less concerned about the spread when in an opposing party CD
```{r}
dvr_concern_model <- glm(binary_concern_strong ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_concern_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_concern_plot <- ggplot(selected_coeff, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.2) +
  coord_flip() +
  labs(y = "Odds Ratio", x = "", title = "Partisan Concern of Spread of Coronavirus Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red")) 

print(dvr_concern_plot)

# View the model summary
summary(dvr_concern_model)
rm(dvr_concern_model)
```
However, being in an opposing CD doesn't mean you're less likely to report contact
Independents are having the most contact
Democrats are not more or less likely to have contact with people in different settings
```{r}
dvr_contact_model <- lm(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_contact_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_contact_plot <- ggplot(selected_coeff, aes(x = term, y = estimate, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = estimate - std.error*1.96, 
                    ymax = estimate + std.error*1.96), width = 0.2) +
  coord_flip() +
  labs(y = "Number of Non-Household Contacts", x = "", title = "Partisan Differences in Non-Household Contacts Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red"))

print(dvr_contact_plot)

# View the model summary
summary(dvr_contact_model)
rm(dvr_contact_model)
```
Democrats are less likely to wear masks when they're in Republican districts
Republicans are more likely to wear masks when they're in Democratic districts
Suggesting some peer pressure effects based on majority
```{r}
dvr_masked_contact_model <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_masked_contact_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_masked_contact_plot <- ggplot(selected_coeff, aes(x = term, y = estimate, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = estimate - std.error*1.96, 
                    ymax = estimate + std.error*1.96), width = 0.2) +
  coord_flip() +
  labs(y = "Number of Non-Household Contacts", x = "", title = "Partisan Differences in Non-Household Mask-Wearing Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks(),
                     limits = c(NA,0)) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red"))

print(dvr_masked_contact_plot)

# View the model summary
summary(dvr_masked_contact_model)
rm(dvr_masked_contact_model)
```
Overall, they're less likely to be safe in their contacts
```{r}
dvr_safety_model <- lm(Non_Weighted_Safety_Index ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_safety_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_safety_plot <- ggplot(selected_coeff, aes(x = term, y = estimate, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = estimate - std.error*1.96, 
                    ymax = estimate + std.error*1.96), width = 0.2) +
  coord_flip() +
  labs(y = "Number of Non-Household Contacts", x = "", title = "Partisan Differences in Non-Household Safety Precautions Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks(),
                     limits = c(NA,.01)) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red"))

print(dvr_safety_plot)

# View the model summary
summary(dvr_safety_model)
rm(dvr_safety_model)
```

```{r}
dvr_vax_model <- glm(Vaccinated ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = df, family = binomial)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(dvr_vax_model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
dvr_vax_plot <- ggplot(selected_coeff, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.2) +
  coord_flip() +
  labs(y = "Odds Ratio", x = "", title = "Partisan Vaccination Across Opposing Party Districts",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks(),
                     limits = c(NA, 1.5)) +
  theme_minimal() +
  theme(legend.position = "none")+
  scale_color_manual(values = c("blue", "magenta", "red")) 

print(dvr_vax_plot)

# View the model summary
summary(dvr_vax_model)
rm(dvr_vax_model)
```

