---
title: "Model Test for Number of Non-HH contacts"
author: "Christopher Soria"
date: "2023-11-21"
output: html_document
---
```{r}
df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
D_df <- df[df$political_party == "Democrat"]
R_df <- df[df$political_party == "Republican"]

names(df) <- make.unique(names(df))
names(RD_df) <- make.unique(names(RD_df))
names(D_df) <- make.unique(names(D_df))
names(R_df) <- make.unique(names(R_df))
```


linear model does fine for num_cc_nonnhh but not a clear linear association
We see the opposite relationship for Democrats and Republicans
Implying that Democrats are more likely to have outside household contacts in regions where more people voted R
Futher, Republicans are less likely to have outside household contacts in regions where more people voted D
What I'm seeing here is that every 10% increase in Trump against Biden vote percentage in the county is associated with .2 more non-household contacts
Every 10% increase in Biden against Trump vote percentage in the county is associated with a .7 reduction in non-household contacts
```{r}
D_model_contacts <- lm(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race, data = D_df)

plot(D_df$republican_percentage_won, D_df$num_cc_nonhh, 
     xlab = "Republican Percentage Won", ylab = "Non-Household Contacts",
     main = "plot of Non-HH Contacts on Republican Percentage Won")

abline(D_model_contacts, col = "blue")

R_model_contacts <- lm(num_cc_nonhh ~ democrat_percentage_won + COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + resp_educ + resp_yob + r_working + r_race, data = R_df)

plot(R_df$democrat_percentage_won, R_df$num_cc_nonhh, 
     xlab = "Democrat Percentage Won", ylab = "Non-Household Contacts",
     main = "Linear Regression of Non-HH Contacts on Democrat Percentage Won")

abline(R_model_contacts, col = "blue")

print(summary(R_model_contacts))
print(summary(D_model_contacts))
```
Let's try everything in a poisson
Given the large maximum deviance residual and the high residual deviance, this suggests overdispersion, which could indicate that a Negative Binomial model would be more appropriate.

```{r}
D_model_poisson <- glm(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + 
                       State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + 
                       resp_educ + resp_yob + r_working + r_race, 
                       family = "poisson", data = D_df)

R_model_poisson <- glm(num_cc_nonhh ~ democrat_percentage_won + COV_County_CMR_2020_06_20 + 
                       State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + 
                       resp_educ + resp_yob + r_working + r_race, 
                       family = "poisson", data = R_df)

print(summary(D_model_poisson))
print(summary(R_model_poisson))
```
confirmation that a poisson model is not great
```{r}
D_dispersion <- sum(residuals(D_model_poisson, type = "pearson")^2)
R_dispersion <- sum(residuals(R_model_poisson, type = "pearson")^2)

# Degrees of freedom
D_df_free <- df.residual(D_model_poisson)
R_df_free <- df.residual(R_model_poisson)

# Dispersion parameter
D_dispersion_parameter <- D_dispersion / D_df_free
R_dispersion_parameter <- R_dispersion / R_df_free

# Output the dispersion parameter for both models
D_dispersion_parameter
R_dispersion_parameter
```
let's try a negative binomial
AIC is much lower here (indicating a better fit)

```{r}
library(MASS)

# Convert the Poisson models to Negative Binomial models
D_model_negbin <- glm.nb(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + 
                         State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + 
                         resp_educ + resp_yob + r_working + r_race, data = D_df)

R_model_negbin <- glm.nb(num_cc_nonhh ~ democrat_percentage_won + COV_County_CMR_2020_06_20 + 
                         State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + 
                         resp_educ + resp_yob + r_working + r_race, data = R_df)

# Print the summaries of the Negative Binomial models
print(summary(D_model_negbin))
print(summary(R_model_negbin))
```
Let's do some further tests of the negative binomial
The residuals seem to fan out as the fitted values increase, indicating potential heteroscedasticity
There are a few points with very high residuals. These may be outliers or influential points that could be disproportionately affecting the model.
There seems to be a large cluster of residuals near zero for low fitted values, which might suggest zero inflation.
```{r}
plot(fitted(D_model_negbin), residuals(D_model_negbin, type = "pearson"),
     xlab = "Fitted Values", ylab = "Pearson Residuals",
     main = "Residuals vs Fitted")
abline(h = 0, col = "red")
```

This suggest that there might be some extreme outliers in the data
```{r}
qqnorm(residuals(D_model_negbin, type = "pearson"))
qqline(residuals(D_model_negbin, type = "pearson"), col = "red")
```
let's see what the extreme outliers are
Some people are saying they had 99 contacts
```{r}
summary(D_df$num_cc_nonhh)
plot(table(D_df$num_cc_nonhh))
```
```{r}
plot(fitted(D_model_negbin), sqrt(abs(residuals(D_model_negbin, type = "pearson"))),
     xlab = "Fitted Values", ylab = "Square Root of |Pearson Residuals|",
     main = "Scale-Location Plot")
```

```{r}
# Install and load the 'car' package for leverage plots
if (!requireNamespace("car", quietly = TRUE)) {
    install.packages("car")
}
library(car)
influencePlot(D_model_negbin, id.method = "identify", main = "Leverage Plot")
```

```{r}
summary(D_model_negbin)$theta
```
All things above suggest that the negative binomal does a decent job at modeling this data, however; the presence of a few outliers seems to be complicating things a bit. Let's compare this model to a zero inflated negative binomial (ZIMB)
The very small difference in AIC suggest zero inflation is not improving things much (and is only complicated the interpretation)
However, this test indicates that some of the variables not fit in well with each other
I removed County RUCC (which maybe makes more sense to convert to a binary) and state-level response and things worked well afterwards. 

```{r}
# Install and load the 'pscl' package if it's not already installed
if (!requireNamespace("pscl", quietly = TRUE)) {
    install.packages("pscl")
}
library(pscl)

D_model_negbin <- glm.nb(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + 
                         resp_sex + 
                         resp_educ + resp_yob + r_working + r_race, data = D_df)

# Fit a Zero-Inflated Negative Binomial model
D_model_zinb <- zeroinfl(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + 
                         resp_sex + 
                         resp_educ + resp_yob + r_working + r_race | 1, data = D_df, 
                         dist = "negbin")

# Compare AIC of both models
aic_negbin <- AIC(D_model_negbin)
aic_zinb <- AIC(D_model_zinb)

# Print the AIC for comparison
print(c(aic_negbin, aic_zinb))
```

Let's run a few diagnostic tests (first I'll check VIF)
```{r}
# Convert the Poisson models to Negative Binomial models
D_model_negbin <- glm.nb(num_cc_nonhh ~ republican_percentage_won + COV_County_CMR_2020_06_20 + 
                         State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + resp_sex + 
                         resp_educ + resp_yob + r_working + r_race, data = D_df)

summary(D_model_negbin)

# Install and load the 'car' package for VIF
if (!requireNamespace("car", quietly = TRUE)) {
    install.packages("car")
}
library(car)

# Calculate VIF
vif(D_model_negbin)

```

