---
title: "02-Republican_v_Democrat_Overall"
author: "Christopher Soria"
date: "2024-01-30"
output: html_document
---
```{r}
library(sjPlot)
library(MASS)
library(tidyverse)
```


First, I want to find out who was more likely to say that they reduced contact throughout the pandemic
clustering of errors?
controlling for state?
controlling for binary state variables?
Cluster errors by wave?
```{r}
rvd_contact_reduction_model <- lm(contact_reduction ~  log_rate_prev_12_01_20 + county_mask_mandate + COUNTY_RUCC_2013 + male + educ_group + resp_yob + r_working + Income_Category + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave + extreme_liberal + extreme_conservative, 
                                   data = bics_zip_features,
                                   weights = weight_pooled)

rvd_contact_reduction_plot <- plot_model(
  rvd_contact_reduction_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Contact Reduction Throughout \nthe Pandemic",
  axis.title = c("", "Predicted Probability of Contact Reduction")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 14), 
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_contact_reduction_pooled.png", plot = rvd_contact_reduction_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Contact_Reduction", width = 12, height = 8, units = "in")

summary(rvd_contact_reduction_model)
print(rvd_contact_reduction_plot)

rm(rvd_contact_reduction_model,rvd_contact_reduction_plot)
```
Next, I want to find out who was more concerned about the spread of the virus throughout the pandemic
```{r}
rvd_concern_model <- lm(binary_concern_strong ~  `rate_prev_12/1/20` + county_mask_mandate + COUNTY_RUCC_2013 + male + educ_group + resp_yob + r_working + Income_Category + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave  + extreme_liberal + extreme_conservative, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)


rvd_concern_plot <- plot_model(
  rvd_concern_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Concern about Spread of the Virus \nThroughout the Pandemic",
  axis.title = c("", "Predicted Probability of Concern of Spread")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 14), 
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_concern_pooled.png", plot = rvd_concern_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Concern", width = 12, height = 8, units = "in")

print(summary(rvd_concern_model))
rvd_concern_plot

rm(rvd_concern_model,rvd_concern_plot)
```
Now, let's take a look at number of non-household contacts glm.nb
```{r}
rvd_contacts_model <- glm.nb(num_cc_nonhh  ~  `rate_prev_12/1/20` + county_mask_mandate + COUNTY_RUCC_2013 + male + educ_group + resp_yob + r_working + Income_Category + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave + extreme_liberal + extreme_conservative, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)

print(summary(rvd_contacts_model))

rvd_contacts_plot <- plot_model(
  rvd_contacts_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Non-Household Contacts \nThroughout the Pandemic",
  axis.title = c("", "Predicted Non-Household Contacts")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 14), 
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_contacts_pooled.png", plot = rvd_contacts_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Contacts", width = 12, height = 8, units = "in")

rvd_contacts_plot

rm(rvd_contacts_model,rvd_contacts_plot)
```
And lastly, let's see how republicans and democrats differed on mask usage
For now, I'm using a linear model for the sake of making it easy to interpret 
```{r}
rvd_masks_model <- lm(Norm_Masks_Used  ~  log_rate_prev_12_01_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + male + educ_group + resp_yob + r_working + Income_Category + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave + political_view, 
                                   data = bics_zip_features)

print(plot(rvd_masks_model))
print(car::vif(rvd_masks_model))
print(lmtest::dwtest(rvd_masks_model))
print(summary(rvd_masks_model))

rvd_masks_plot <- plot_model(
  rvd_masks_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Proportion of Non-Household \nContacts With a Mask on Throughout the Pandemic",
  axis.title = c("", "Predicted Proportion of Contacts with a Mask")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 14), 
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_masks_pooled.png", plot = rvd_masks_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Masks", width = 12, height = 8, units = "in")

rvd_masks_plot

rm(rvd_masks_model,rvd_masks_plot)
```
Vaccines
```{r}
rvd_vaccination_model <- lm(Vaccinated  ~  log_rate_prev_12_01_20 + State_Government_Response_Index_11192020 + COUNTY_RUCC_2013 + male + educ_group + resp_yob + r_working + Income_Category + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + political_view, 
                                   data = bics_zip_features)

print(plot(rvd_vaccination_model))
print(car::vif(rvd_vaccination_model))
print(lmtest::dwtest(rvd_vaccination_model))
print(summary(rvd_vaccination_model))

rvd_vaccination_plot <- plot_model(
  rvd_vaccination_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Proportion Vaccinated as of 5/21",
  axis.title = c("", "Predicted Proportion of Contacts with a Mask")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 14), 
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_vaccines_pooled.png", plot = rvd_vaccination_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Vaccines", width = 12, height = 8, units = "in")

rvd_vaccination_plot

rm(rvd_vaccination_model,rvd_vaccination_plot)
```

