---
title: "02-Republican_v_Democrat_Overall"
author: "Christopher Soria"
date: "2024-01-30"
output: html_document
---
```{r}
library(sjPlot)
library(MASS)
library(tidyverse)
library(emmeans)

emm_options(rg.limit = 250000)
dodge_width = .7
```
```{r}

```


First, I want to find out who was more likely to say that they reduced contact throughout the pandemic
clustering of errors?
controlling for state?
controlling for binary state variables?
Cluster errors by wave?
```{r}
rvd_contact_reduction_model <- lm(contact_reduction ~  log_rate_prev_12_01_20 + county_mask_mandate + COUNTY_RUCC_2013 + male + educ_group + resp_yob + resp_hhsize + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave, 
                                   data = bics_zip_features,
                                   weights = weight_pooled)

rvd_contact_reduction_plot <- plot_model(
  rvd_contact_reduction_model,
  colors = "black",
  type = "pred",
  auto.label = FALSE,
  terms = c("political_party[Democrat, Republican, Independent]"),
  title = "Partisan Differences in Contact Reduction Throughout \nthe Pandemic",
  axis.title = c("", "Predicted Probability of Contact Reduction")
) +
theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.y = element_text(size = 20), 
    axis.title.y = element_text(size = 20), 
    axis.text.x = element_text(size = 15), 
    axis.text.y = element_text(size = 13),
    axis.title.x = element_text(size = 14),  
    plot.title = element_text(size = 28, face = "bold"), 
    plot.subtitle = element_text(size = 15)
  ) +
  geom_point(size = 5) 

ggsave("rvd_contact_reduction_pooled.png", plot = rvd_contact_reduction_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Contact_Reduction", width = 12, height = 8, units = "in")

summary(rvd_contact_reduction_model)
print(rvd_contact_reduction_plot)

rm(rvd_contact_reduction_model,rvd_contact_reduction_plot)
```
Next, I want to find out who was more concerned about the spread of the virus throughout the pandemic
```{r}
rvd_concern_model <- lm(binary_concern_strong ~  log_current_week_inc_rate + county_mask_mandate + COUNTY_RUCC_2013 + male + educ_group + resp_yob + resp_hhsize + r_race + political_party + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta + wave, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)


emm_concern <- emmeans(rvd_concern_model, specs = "political_party")
emm_concern <- transform(summary(emm_concern))

emm_concern <- emm_concern %>% 
  filter(political_party != "Prefer not to answer")

rvd_concern_plot <- ggplot(emm_concern, aes(x = political_party, y = emmean, color = political_party, shape = political_party)) +
  geom_point(position = position_dodge(width = 0.35), size = 4) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen")) +
  labs(y = "Probability of Concern", x = "", color = "Political Party", title = "Predicted Probablity of Being 'Very Concerned' About Spread") +  # Make sure to add your title here
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, position = position_dodge(width = 0.35)) +
  theme_minimal() +
  theme(legend.position = "none",
        plot.title = element_text(size = 26),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 13),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10)) +
  guides(shape = "none")

ggsave("rvd_concern_pooled.png", plot = rvd_concern_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Concern", width = 12, height = 8, units = "in")

print(summary(rvd_concern_model))
rvd_concern_plot

rm(rvd_concern_model,rvd_concern_plot)
```
Now, let's take a look at number of non-household contacts
```{r}
emm_options(rg.limit = 500000)

rvd_contacts_model <- lm(num_cc_nonhh ~ log_prev_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + political_party + r_working + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + wave + binary_concern_strong, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)
print(summary(rvd_contacts_model))

emm_contacts <- emmeans(rvd_contacts_model, specs = "political_party", 
                        at = list(log_prev_week_inc_rate = weighted.mean(bics_zip_features$log_prev_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  county_mask_mandate = "Strict",
                                  educ_group = "College graduate and above",
                                  Metro = 1,
                                  Male = 1,
                                  r_race = "White",
                                  r_working = "Working",
                                  cityNY = 0,
                                  `cityBay Area` = 0,
                                  cityPhiladelphia = 0,
                                  cityPhoenix = 0,
                                  cityBoston = 0,
                                  cityAtlanta = 0))

emm_contacts <- transform(summary(emm_contacts))

emm_contacts$controls <- "controls"

rvd_contacts_model_raw <- lm(num_cc_nonhh ~ political_party + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)

emm_contacts_raw <- emmeans(rvd_contacts_model_raw, specs = "political_party", 
                        at = list(log_prev_week_inc_rate = weighted.mean(bics_zip_features$log_prev_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  county_mask_mandate = "Strict",
                                  educ_group = "College graduate and above",
                                  Metro = 1,
                                  Male = 1,
                                  r_race = "White",
                                  r_working = "Working",
                                  cityNY = 0,
                                  `cityBay Area` = 0,
                                  cityPhiladelphia = 0,
                                  cityPhoenix = 0,
                                  cityBoston = 0,
                                  cityAtlanta = 0))

emm_contacts_raw <- transform(summary(emm_contacts_raw))

emm_contacts_raw$controls <- "baseline"

emm_contacts <- emm_contacts %>% 
  filter(political_party != "Prefer not to answer")

emm_contacts_raw <- emm_contacts_raw %>% 
  filter(political_party != "Prefer not to answer")

all_emms <- rbind(emm_contacts_raw, emm_contacts)

rvd_contacts_plot <- ggplot(all_emms, aes(x = political_party, y = emmean, color = political_party, group = interaction(political_party, controls))) +
  geom_point(aes(shape = controls, size = controls), position = position_dodge(width = dodge_width)) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen", "blue", "red", "darkgreen")) +
  scale_shape_manual(name = NULL, values = c("baseline" = 1, "controls" = 16), labels = c("unadjusted", "adjusted")) +
  scale_size_manual(values = c("baseline" = 6, "controls" = 6), labels = c("unadjusted", "adjusted")) +
  labs(y = "", x = "", color = "Political Party", title = "predicted number of daily contacts") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, position = position_dodge(width = dodge_width)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 22)) +
  guides(shape = guide_legend(override.aes = list(size = 6)),
         color = "none", 
         size = "none")

ggsave("rvd_contacts_pooled.png", plot = rvd_contacts_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Contacts", width = 12, height = 8, units = "in")

rvd_contacts_plot

rm(rvd_contacts_model, rvd_contacts_plot, all_emms, emm_contacts, emm_contacts_raw,rvd_contacts_model_raw)
```
And lastly, let's see how republicans and democrats differed on mask usage
For now, I'm using a linear model for the sake of making it easy to interpret 
```{r}
rvd_masks_model <- lm(Norm_Masks_Used  ~ political_party + log_prev_week_inc_rate + county_mask_mandate + as.factor(Metro) + as.factor(male) + educ_group + resp_yob + resp_hhsize + r_race + r_working + as.factor(cityNY) + as.factor(`cityBay Area`) + as.factor(cityPhiladelphia) + as.factor(cityPhoenix) + as.factor(cityBoston) + as.factor(cityAtlanta) + as.factor(wave), 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)
print(summary(rvd_masks_model))

emm_masks <- emmeans(rvd_masks_model, specs = pairwise ~ political_party | wave, 
                     at = list(log_prev_week_inc_rate = weighted.mean(bics_zip_features$log_prev_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                               resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                               resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                               county_mask_mandate = "Strict",
                               educ_group = "College graduate and above",
                               Metro = 1,
                               Male = 1,
                               r_race = "White",
                               r_working = "Working",
                               cityNY = 0,
                               `cityBay Area` = 0,
                               cityPhiladelphia = 0,
                               cityPhoenix = 0,
                               cityBoston = 0,
                               cityAtlanta = 0))


emm_masks <- transform(summary(emm_masks))
emm_masks$controls <- "controls"

rvd_masks_model_raw <- lm(Norm_Masks_Used  ~ political_party + as.factor(cityNY) + as.factor(`cityBay Area`) + as.factor(cityPhiladelphia) + as.factor(cityPhoenix) + as.factor(cityBoston) + as.factor(cityAtlanta), 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)

emm_masks_raw <- emmeans(rvd_masks_model_raw, specs = "political_party", 
                        at = list(log_prev_week_inc_rate = weighted.mean(bics_zip_features$log_prev_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  county_mask_mandate = "Strict",
                                  educ_group = "College graduate and above",
                                  Metro = 1,
                                  Male = 1,
                                  wave = 3,
                                  r_race = "White",
                                  r_working = "Working",
                                  cityNY = 0,
                                  `cityBay Area` = 0,
                                  cityPhiladelphia = 0,
                                  cityPhoenix = 0,
                                  cityBoston = 0,
                                  cityAtlanta = 0))

emm_masks_raw <- transform(summary(emm_masks_raw))

emm_masks_raw$controls <- "baseline"

emm_masks <- emm_masks %>% 
  filter(political_party != "Prefer not to answer")

emm_masks_raw <- emm_masks_raw %>% 
  filter(political_party != "Prefer not to answer")

all_emms <- rbind(emm_masks_raw, emm_masks)

rvd_masks_plot <- ggplot(all_emms, aes(x = political_party, y = emmean, color = political_party, group = interaction(political_party, controls))) +
  geom_point(aes(shape = controls, size = controls), position = position_dodge(width = dodge_width)) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen", "blue", "red", "darkgreen")) +
  scale_shape_manual(name = NULL, values = c("baseline" = 1, "controls" = 16), labels = c("unadjusted", "adjusted")) +
  scale_size_manual(values = c("baseline" = 6, "controls" = 6), labels = c("unadjusted", "adjusted")) +
  labs(y = "", x = "", color = "Political Party", title = "predicted percentage of contacts masked") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, position = position_dodge(width = dodge_width)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 22)) +
  guides(shape = guide_legend(override.aes = list(size = 6)),
         color = "none", 
         size = "none")

ggsave("rvd_masks_pooled.png", plot = rvd_masks_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Masks", width = 12, height = 8, units = "in")

rvd_masks_plot

rm(rvd_masks_model,rvd_masks_plot)
```
Vaccines
```{r}
rvd_vaccines_model <- lm(Vaccinated  ~ political_party + log_prev_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + r_working + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta,
                                   data = bics_zip_features, 
                                   weights = weight_pooled)

emm_vaccines <- emmeans(rvd_vaccines_model, specs = "political_party", 
                        at = list(log_prev_week_inc_rate = weighted.mean(bics_zip_features$log_prev_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  county_mask_mandate = "Strict",
                                  Metro = 1,
                                  Male = 1,
                                  r_race = "White",
                                  wave = 4,
                                  cityNY = 0,
                                  `cityBay Area` = 0,
                                  cityPhiladelphia = 0,
                                  cityPhoenix = 0,
                                  cityBoston = 0,
                                  cityAtlanta = 0))
emm_vaccines <- transform(summary(emm_vaccines))

emm_vaccines$controls <- "controls"
rvd_vaccines_model_raw <- lm(Vaccinated  ~ political_party + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                                   data = bics_zip_features, 
                                   weights = weight_pooled)

emm_vaccines_raw <- emmeans(rvd_vaccines_model_raw, specs = "political_party", 
                        at = list(log_current_week_inc_rate = weighted.mean(bics_zip_features$log_current_week_inc_rate, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_yob = weighted.mean(bics_zip_features$resp_yob, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  resp_hhsize = weighted.mean(bics_zip_features$resp_hhsize, w = bics_zip_features$weight_pooled, na.rm = TRUE),
                                  county_mask_mandate = "Strict",
                                  Metro = 1,
                                  Male = 1,
                                  r_race = "White",
                                  wave = 4,
                                  cityNY = 0,
                                  `cityBay Area` = 0,
                                  cityPhiladelphia = 0,
                                  cityPhoenix = 0,
                                  cityBoston = 0,
                                  cityAtlanta = 0))
emm_vaccines_raw <- transform(summary(emm_vaccines_raw))

emm_vaccines_raw$controls <- "baseline"

emm_vaccines <- emm_vaccines %>% 
  filter(political_party != "Prefer not to answer")

emm_vaccines_raw <- emm_vaccines_raw %>% 
  filter(political_party != "Prefer not to answer")

all_emms <- rbind(emm_vaccines_raw, emm_vaccines)

rvd_vaccination_plot <- ggplot(all_emms, aes(x = political_party, y = emmean, color = political_party, group = interaction(political_party, controls))) +
  geom_point(aes(shape = controls, size = controls), position = position_dodge(width = dodge_width)) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen", "blue", "red", "darkgreen")) +
  scale_shape_manual(name = NULL, values = c("baseline" = 1, "controls" = 16), labels = c("unadjusted", "adjusted")) +
  scale_size_manual(values = c("baseline" = 6, "controls" = 6), labels = c("unadjusted", "adjusted")) +
  labs(y = "", x = "", color = "Political Party", title = "predicted probability of vaccination") +
  geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), width = 0.2, position = position_dodge(width = dodge_width)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 22)) +
  guides(shape = guide_legend(override.aes = list(size = 6)),
         color = "none", 
         size = "none")

ggsave("rvd_vaccines_pooled.png", plot = rvd_vaccination_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Vaccines", width = 12, height = 8, units = "in")

rvd_vaccination_plot

rm(rvd_vaccination_model,rvd_vaccination_plot)
```
Below, I want to find out who is more responsive to incidence rates (democrats or republicans)
After controls, neither is more or less responsive to incidence rates than the other when it comes to mask usage.
```{r}
bi_mask_dem <- lm(Norm_Masks_Used ~ current_week_inc_rate + wave + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = D_df, 
                  weights = weight_pooled)
print(summary(bi_mask_dem))

bi_mask_dem_raw <- lm(Norm_Masks_Used ~ current_week_inc_rate + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                      data = D_df, 
                      weights = weight_pooled)
print(summary(bi_mask_dem_raw))

bi_mask_rep <- lm(Norm_Masks_Used ~ current_week_inc_rate + wave + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = R_df, 
                  weights = weight_pooled)
print(summary(bi_mask_rep))

bi_mask_rep_raw <- lm(Norm_Masks_Used ~ current_week_inc_rate + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, data = R_df, weights = weight_pooled)

bi_mask_ind <- lm(Norm_Masks_Used ~ current_week_inc_rate + wave + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = I_df, 
                  weights = weight_pooled)
print(summary(bi_mask_ind))

bi_mask_ind_raw <- lm(Norm_Masks_Used ~ current_week_inc_rate + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, data = I_df, weights = weight_pooled)

coef_dem <- summary(bi_mask_dem)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_rep <- summary(bi_mask_rep)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_ind <- summary(bi_mask_ind)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_dem_raw <- summary(bi_mask_dem_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_rep_raw <- summary(bi_mask_rep_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_ind_raw <- summary(bi_mask_ind_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]

coef_df <- data.frame(
  political_party = c("Democrat", "Republican", "Independent"),
  Estimate = c(coef_dem[1], coef_rep[1], coef_ind[1]),
  SE = c(coef_dem[2], coef_rep[2], coef_ind[2]),
  controls = "controls"
)

coef_df_raw <- data.frame(
  political_party = c("Democrat", "Republican", "Independent"),
  Estimate = c(coef_dem_raw[1], coef_rep_raw[1], coef_ind_raw[1]),
  SE = c(coef_dem_raw[2], coef_rep_raw[2], coef_ind_raw[2]),
  controls = "baseline"
)

all_ceofs <- rbind(coef_df_raw,coef_df)

all_ceofs$political_party <- factor(coef_df$political_party, levels = c("Democrat", "Republican", "Independent"))

rvd_response_masks_plot <- ggplot(all_ceofs, aes(x = political_party, y = Estimate, color = political_party, group = interaction(political_party, controls))) +
  geom_point(aes(shape = controls, size = controls), position = position_dodge(width = dodge_width)) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen", "blue", "red", "darkgreen")) +
  scale_shape_manual(name = NULL, values = c("baseline" = 1, "controls" = 16), labels = c("unadjusted", "adjusted")) +
  scale_size_manual(values = c("baseline" = 6, "controls" = 6), labels = c("unadjusted", "adjusted")) +
  labs(y = "", x = "", color = "Political Party", title = "mask usage in response to new cases") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.2, position = position_dodge(width = dodge_width)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 22)) +
  guides(shape = guide_legend(override.aes = list(size = 6)),
         color = "none", 
         size = "none")

ggsave("rvd_incidence_response.png", plot = rvd_response_masks_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Masks", width = 12, height = 8, units = "in")

rvd_response_masks_plot

rm(emm_both,rvd_response_masks_plot)

rm(bi_mask_dem,bi_mask_rep, bi_mask_ind, coef_df)
```

```{r}
bi_mask_dem_w2 <- lm(Norm_Masks_Used ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = subset(D_df, wave == 2), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w2))

bi_mask_dem_w3 <- lm(Norm_Masks_Used ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = subset(D_df, wave == 3), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w3))

bi_mask_dem_w4 <- lm(Norm_Masks_Used ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = subset(D_df, wave == 4), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w4))

bi_mask_dem_w5 <- lm(Norm_Masks_Used ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = subset(D_df, wave == 5), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w5))

bi_mask_dem_w6 <- lm(Norm_Masks_Used ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                  data = subset(D_df, wave == 6), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w6))

coeff_w2 <- coef(summary(bi_mask_dem_w2))["current_week_inc_rate", ]
coeff_w3 <- coef(summary(bi_mask_dem_w3))["current_week_inc_rate", ]
coeff_w4 <- coef(summary(bi_mask_dem_w4))["current_week_inc_rate", ]
coeff_w5 <- coef(summary(bi_mask_dem_w5))["current_week_inc_rate", ]
coeff_w6 <- coef(summary(bi_mask_dem_w6))["current_week_inc_rate", ]

coefficients_df <- data.frame(
  wave = 2:6,
  estimate = c(coeff_w2[1], coeff_w3[1], coeff_w4[1], coeff_w5[1], coeff_w6[1]),
  std_error = c(coeff_w2[2], coeff_w3[2], coeff_w4[2], coeff_w5[2], coeff_w6[2]),
  t_value = c(coeff_w2[3], coeff_w3[3], coeff_w4[3], coeff_w5[3], coeff_w6[3]),
  p_value = c(coeff_w2[4], coeff_w3[4], coeff_w4[4], coeff_w5[4], coeff_w6[4])
)

ggplot(coefficients_df, aes(x = factor(wave), y = estimate, color = factor(wave))) +
  geom_point() +
  geom_errorbar(aes(ymin = estimate - std_error, ymax = estimate + std_error), width = 0.1) +
  labs(x = "Wave", y = "Coefficient of log_current_week_inc_rate",
       title = "Coefficient of log_current_week_inc_rate Across Waves") +
  theme_minimal() +
  scale_color_brewer(palette = "Set1")  # Colors to distinguish waves
```

```{r}
options(max.print = 10000)
bi_mask_dem_w2 <- lm(Norm_Masks_Used ~  + as.factor(COUNTY_FIPS) + log_current_week_inc_rate*political_party + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + wave, 
                  data = subset(bics_zip_features), 
                  weights = weight_pooled)

bi_mask_dem_w3 <- lm(Norm_Masks_Used ~  + log_current_week_inc_rate*political_party + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features), 
                  weights = weight_pooled)

print(summary(bi_mask_dem_w3))
```


```{r}
bi_mask_rep_w2 <- lm(Norm_Masks_Used ~ log_current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features, wave == 2), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w2))

bi_mask_dem_w3 <- lm(Norm_Masks_Used ~ log_current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features, wave == 3), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w3))

bi_mask_dem_w4 <- lm(Norm_Masks_Used ~ log_current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features, wave == 4), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w4))

bi_mask_dem_w5 <- lm(Norm_Masks_Used ~ log_current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features, wave == 5), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w5))

bi_mask_dem_w6 <- lm(Norm_Masks_Used ~ log_current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta, 
                  data = subset(bics_zip_features, wave == 6), 
                  weights = weight_pooled)
print(summary(bi_mask_dem_w6))
```


However, when it comes to contact rates Republicans are much more responsive. Where Democrats are more likely to keep rates low.
```{r}
bi_contact_dem <- lm(num_cc_nonhh ~ current_week_inc_rate + wave + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + as.factor(COUNTY_FIPS), 
                     data = D_df, 
                     weights = weight_pooled)
print(summary(bi_contact_dem))

bi_contact_dem_raw <- lm(num_cc_nonhh ~ current_week_inc_rate + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta, data = D_df, weights = weight_pooled)

bi_contact_rep <- lm(num_cc_nonhh ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + wave + as.factor(COUNTY_FIPS), 
                     data = R_df, 
                     weights = weight_pooled)
print(summary(bi_contact_rep))

bi_contact_rep_raw <- lm(num_cc_nonhh ~ current_week_inc_rate + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta, data = R_df, weights = weight_pooled)

bi_contact_ind <- lm(num_cc_nonhh ~ current_week_inc_rate + county_mask_mandate + Metro + male + educ_group + resp_yob + resp_hhsize + r_race + cityNY + `cityBay Area` + cityPhiladelphia + cityPhoenix + cityBoston + cityAtlanta + wave + as.factor(COUNTY_FIPS), 
                     data = I_df, 
                     weights = weight_pooled)
print(summary(bi_contact_ind))

bi_contact_ind_raw <- lm(num_cc_nonhh ~ current_week_inc_rate + cityNY +`cityBay Area` +cityPhiladelphia + cityPhoenix +cityBoston + cityAtlanta, data = I_df, weights = weight_pooled)

coef_dem <- summary(bi_contact_dem)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_rep <- summary(bi_contact_rep)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_ind <- summary(bi_contact_ind)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_dem_raw <- summary(bi_contact_dem_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_rep_raw <- summary(bi_contact_rep_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]
coef_ind_raw <- summary(bi_contact_ind_raw)$coefficients["current_week_inc_rate", c("Estimate", "Std. Error")]

coef_df <- data.frame(
  political_party = c("Democrat", "Republican", "Independent"),
  Estimate = c(coef_dem[1], coef_rep[1], coef_ind[1]),
  SE = c(coef_dem[2], coef_rep[2], coef_ind[2]),
  controls = "controls"
)

coef_df_raw <- data.frame(
  political_party = c("Democrat", "Republican", "Independent"),
  Estimate = c(coef_dem_raw[1], coef_rep_raw[1], coef_ind_raw[1]),
  SE = c(coef_dem_raw[2], coef_rep_raw[2], coef_ind_raw[2]),
  controls = "baseline"
)

all_ceofs <- rbind(coef_df_raw,coef_df)

all_ceofs$political_party <- factor(coef_df$political_party, levels = c("Democrat", "Republican", "Independent"))

rvd_response_contacts_plot <- ggplot(all_ceofs, aes(x = political_party, y = Estimate, color = political_party, group = interaction(political_party, controls))) +
  geom_point(aes(shape = controls, size = controls), position = position_dodge(width = dodge_width)) +
  scale_color_manual(name = "Political Party", values = c("blue", "red", "darkgreen", "blue", "red", "darkgreen")) +
  scale_shape_manual(name = NULL, values = c("baseline" = 1, "controls" = 16), labels = c("unadjusted", "adjusted")) +
  scale_size_manual(values = c("baseline" = 6, "controls" = 6), labels = c("unadjusted", "adjusted")) +
  labs(y = "", x = "", color = "Political Party", title = "contact reduction in response to new cases") +
  geom_errorbar(aes(ymin = Estimate - SE, ymax = Estimate + SE), width = 0.2, position = position_dodge(width = dodge_width)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 22),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_line(color = "grey70", size = 0.5),
        panel.grid.major.y = element_line(color = "grey90", size = 0.5),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 22),
        axis.text.y = element_text(size = 22),
        axis.title.y = element_text(size = 16),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 22)) +
  guides(shape = guide_legend(override.aes = list(size = 6)),
         color = "none", 
         size = "none")

ggsave("rvd_incidence_response.png", plot = rvd_response_contacts_plot, path = "/Users/chrissoria/Documents/Research/BICS_Political_Polarization/plots/Contacts", width = 12, height = 8, units = "in")

rvd_response_contacts_plot

rm(emm_both,rvd_response_contacts_plot)

rm(bi_contact_dem,bi_contact_rep, bi_contact_ind,coef_df)
rm(bi_contact_dem_raw, bi_contact_rep_raw, bi_contact_ind_raw)
```

```{r}
rm(all_ceofs, coef_df_raw, coef_df)
```

