---
title: "Untitled"
author: "Christopher Soria"
date: "2023-07-25"
output: html_document
---

```{r}
library(data.table)
library(dplyr)
library(tidyverse)
library(car)
```

50 variables in lucid but 62 in lucid-pipeline
```{r}
df_all_waves <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/df_all_waves.rds")
df_all_waves2 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid/df_all_waves.rds")
```
I don't see all the variables here?
```{r}
colnames(df_all_waves)
```


```{r}
setdiff(names(df_all_waves), names(df_all_waves2))
```
So many NA's?
```{r}
table(df_all_waves$political_view, useNA = "always")
```
```{r}
df_w1 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave1_unweighted.rds")
df_w3 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave3_unweighted.rds")
df_w6 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave6_unweighted.rds")
df_w2 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave2_unweighted.rds")
df_w4 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave4_unweighted.rds")
df_w5 <- readRDS("/Users/chrissoria/documents/research/BICs/bics-data/data/lucid-pipeline/national_wave5_unweighted.rds")
df_w1$wave <- 1
df_w2$wave <- 2
df_w3$wave <- 3
df_w4$wave <- 4
df_w5$wave <- 5
df_w6$wave <- 6
```
Can't use w1 because lots of NA for political view?
marketplace you can target specific subgroups
just want a nationally representative sample, use theoreum plus standard set of questions from 
I'm seeing some variables in some waves but not in others?

```{r}
# Check and convert if column exists in df_w2
if ("resp_employ" %in% colnames(df_w1)) {
  df_w1$resp_employ <- as.character(df_w1$resp_employ)
}

if ("resp_employ" %in% colnames(df_w2)) {
  df_w2$resp_employ <- as.character(df_w2$resp_employ)
}

if ("resp_employ" %in% colnames(df_w3)) {
  df_w3$resp_employ <- as.character(df_w3$resp_employ)
}

# Check and convert if column exists in df_w4
if ("resp_employ" %in% colnames(df_w4)) {
  df_w4$resp_employ <- as.character(df_w4$resp_employ)
}

if ("resp_employ" %in% colnames(df_w5)) {
  df_w5$resp_employ <- as.character(df_w5$resp_employ)
}

# Check and convert if column exists in df_w6
if ("resp_employ" %in% colnames(df_w6)) {
  df_w6$resp_employ <- as.character(df_w6$resp_employ)
}

```

```{r}
df_w2$resp_occupation <- as.character(df_w2$resp_occupation)
df_w3$resp_occupation <- as.character(df_w3$resp_occupation)
df_w4$resp_occupation <- as.character(df_w4$resp_occupation)
df_w5$resp_occupation <- as.character(df_w5$resp_occupation)

df_combined <- dplyr::bind_rows(df_w2, df_w3, df_w4, df_w5, df_w6)
write.csv(df_combined, file = "df_combined.csv", row.names = FALSE)
```

```{r}
# Defining the mapping
political_view_mapping <- c('Extremely conservative' = 1,
                            'Slightly conservative' = 2,
                            'Moderate' = 3,
                            'Middle of the road' = 3,
                            'Slightly liberal' = 4,
                            'Liberal' = 5,
                            'Extremely liberal' = 6)

# Creating a new variable 'political_view_numeric' by mapping the 'political_view' column using the defined mapping
df_combined$political_view_numeric <- dplyr::recode(df_combined$political_view, !!!political_view_mapping)
```

```{r}
df_combined %>%
  group_by(wave) %>%
  summarise(avg_political_view = mean(political_view_numeric, na.rm = TRUE))


```

political view gets more liberal over time between wave 1 - 6
conservatives dropped out? 
```{r}
df_combined$wave <- as.factor(df_combined$wave)

df_list <- split(df_combined, df_combined$wave)

plots <- lapply(df_list, function(df) {
  df$political_view_numeric <- as.factor(df$political_view_numeric)
  total <- nrow(df)
  
  df_percent <- df %>%
    group_by(political_view_numeric) %>%
    summarise(count = n()) %>%
    mutate(percentage = count / total * 100)
  
  ggplot(df_percent, aes(x = political_view_numeric, y = percentage)) +
    geom_bar(stat = "identity") +
    ylab("Percentage") +
    ggtitle(paste0("Wave ", unique(df$wave)))
})

# Plotting the plots
gridExtra::grid.arrange(grobs = plots)

# Check homogeneity of variances
leveneTest(political_view_numeric ~ wave, data = df_combined)
```
```{r}
write.csv(df_combined, file = "df_combined.csv", row.names = FALSE)
```

