---
title: "Untitled"
author: "Christopher Soria"
date: "2023-10-02"
output: html_document
---

```{r}
model <- glm(contact_reduction ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + political_party, data = df, family = binomial)

# View the model summary
summary(model)
```

```{r}
model <- glm(contact_reduction ~ political_party + COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + resp_sex + resp_educ + resp_yob, data = df, family = binomial)

# View the model summary
summary(model)
```

```{r}
model <- glm(contact_reduction ~ political_party + CONGRESSPERSON_PARTY + State_Government_Response_Index_11192020 + COV_County_CMR_2020_06_20 + resp_sex + resp_educ + resp_yob, data = df, family = binomial)

# View the model summary
summary(model)

library(broom)
tidy_model <- broom::tidy(model)
```

```{r}
model <- glm(contact_reduction ~ political_party_to_CD + State_Government_Response_Index_11192020 + COV_County_CMR_2020_06_20 + resp_sex + resp_educ + resp_yob, data = df, family = binomial)

# View the model summary
summary(model)

library(broom)
tidy_model <- broom::tidy(model)
```

```{r}
# Load required libraries
library(broom)
library(dplyr)
library(ggplot2)

# Your model
model <- glm(contact_reduction ~ political_party_to_CD + COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + resp_sex + resp_educ + resp_yob + POPESTIMATE2020, 
             data = df, family = binomial)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(model)

# Filter the coefficients you are interested in and calculate odds ratios
selected_coeff <- tidy_model %>%
  filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                     "political_party_to_CDRepublican in Democratic led CD", 
                     "political_party_to_CDRepublican in Republican led CD")) %>%
  mutate(odds_ratio = exp(estimate)) %>%
  mutate(term = ifelse(term == "political_party_to_CDDemocrat in Republican led CD", "Democrat in Republican CD", term)) %>%
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Democratic led CD", "Republican in Democratic CD", term)) %>% 
  mutate(term = ifelse(term == "political_party_to_CDRepublican in Republican led CD", "Republican in Republican CD", term))

# Plot
ggplot(selected_coeff, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), 
                    ymax = exp(estimate + std.error*1.96)), width = 0.2) +
  coord_flip() +
  labs(y = "Odds Ratio", x = "", title = "Odds Ratios of Reporting Reduction in Contact as a Result of the Pandemic",
       subtitle = "Reference Category: Democrats in Democratic led CD") +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  theme_minimal() +
  theme(legend.position = "none")  # This line removes the legend
```
```{r}
library(broom)
library(dplyr)
library(ggplot2)
library(cowplot)  # for combining plots

# Function to create a plot for a given subset of data
create_plot <- function(data_subset) {
  
  model <- glm(contact_reduction ~ political_party_to_CD + CONGRESSPERSON_PARTY + 
                 COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + resp_sex + resp_educ + resp_yob, 
               data = data_subset, family = binomial)

  tidy_model <- broom::tidy(model)

  selected_coeff <- tidy_model %>%
    filter(term %in% c("political_party_to_CDDemocrat in Republican led CD", 
                       "political_party_to_CDRepublican in Democratic led CD", 
                       "political_party_to_CDRepublican in Republican led CD")) %>%
    mutate(odds_ratio = exp(estimate)) %>%
    mutate(term = recode(term,
                         `political_party_to_CDDemocrat in Republican led CD` = "Democrat in Republican CD",
                         `political_party_to_CDRepublican in Democratic led CD` = "Republican in Democratic CD",
                         `political_party_to_CDRepublican in Republican led CD` = "Republican in Republican CD"))

  ggplot(selected_coeff, aes(x = reorder(term, odds_ratio), y = odds_ratio, color = term)) +
    geom_point(size = 4) +
    geom_errorbar(aes(ymin = exp(estimate - std.error*1.96), ymax = exp(estimate + std.error*1.96)), width = 0.2) +
    coord_flip() +
    labs(y = "Odds Ratio", x = "", 
         title = paste("Wave", unique(data_subset$wave), ": Odds Ratios of Reporting Reduction in Contact"),
         subtitle = "Reference Category: Democrats in Democratic led CD") +
    scale_y_continuous(breaks = scales::pretty_breaks()) +
    theme_minimal() +
    theme(legend.position = "none")
}

# Applying the function to each subset of data by wave and store plots in a list
plots <- df %>% 
  split(.$wave) %>%  # Split data by wave
  map(~create_plot(.))  # Apply the function to each subset

# Combine the separate plots into one
combined_plot <- cowplot::plot_grid(plotlist = plots, align = 'h')

# Print the combined plot
print(combined_plot)
```
```{r}
model_list <- df %>%
  group_by(wave) %>%
  group_split() %>%
  lapply(function(data) lm(num_cc_nonhh ~ political_party + political_view + State_Government_Response_Index_11192020 + COV_County_CMR_2020_06_20 + resp_sex + educ_group + resp_yob + r_working + resp_hispanic + r_race, data = data))

model_summaries <- lapply(model_list, summary)

# wave 2
print(model_summaries[[1]])

# wave 4
print(model_summaries[[2]])

# wave 6
print(model_summaries[[3]])
```

The political view variable is not doing well (need to talk to Ayesha and Dennis about this)
However, we can see that the Republican versus Democrat difference always shows that Republicans are less likely to practice safety precautions after wave 2. In other words, by the end of 2020 Republicans were less likely than Democrats to wear masks, use gloves, and other protective equipment. In Mid 2020 they were MORE likely. 
```{r}
model_list <- df %>%
  group_by(wave) %>%
  group_split() %>%
  lapply(function(data) lm(Non_Weighted_Safety_Index ~ political_party + political_view + State_Government_Response_Index_11192020 + COV_County_CMR_2020_06_20 + resp_sex + educ_group + resp_yob + r_working + resp_hispanic + r_race, data = data))

model_summaries <- lapply(model_list, summary)

# wave 2
print(model_summaries[[1]])

# wave 4
print(model_summaries[[2]])

# wave 6
print(model_summaries[[3]])
```

```{r}
model_list <- df %>%
  group_by(wave) %>%
  group_split() %>%
  lapply(function(data) lm(Norm_Masks_Used ~ political_party_to_CD + State_Government_Response_Index_11192020 + COV_County_CMR_2020_06_20 + resp_sex + educ_group + resp_yob + r_working + resp_hispanic + r_race, data = data))

model_summaries <- lapply(model_list, summary)

# wave 2
print(model_summaries[[1]])

# wave 4
print(model_summaries[[2]])

# wave 6
print(model_summaries[[3]])
```

