---
title: "Non_Household_Contacts"
author: "Christopher Soria"
date: "2023-12-02"
output: html_document
---

```{r}
library(data.table)
library(tidyverse)
library(dplyr)
library(MASS)
library(gridExtra)
library(broom)

df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")
names(df) <- make.unique(names(df))
df$data_collected_dates <- factor(df$data_collected_dates, levels = c("June 18-24, '20", "September 12-20, '20'", "December 1-7, '20'","February 9-14, '21'","May 14-25, '21'"))  

df$Categorical_Dem_CD_County_Share <- factor(
  df$Categorical_Dem_CD_County_Share,
  levels = c("Greater than or Equal to Three Quarters", "Three Quarters", "Two Quarters", "Less Than a Quarter"),
  ordered = FALSE
)

df$Categorical_Repub_CD_County_Share <- factor(
  df$Categorical_Repub_CD_County_Share,
  levels = c("Greater than or Equal to Three Quarters", "Three Quarters", "Two Quarters", "Less Than a Quarter"),
  ordered = FALSE
)

RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
D_df <- df[df$political_party == "Democrat"]
R_df <- df[df$political_party == "Republican"]

D_df <- D_df[D_df$Categorical_Repub_CD_County_Share != ""]
R_df <- R_df[R_df$Categorical_Dem_CD_County_Share != ""]
```
1.6 means that Republicans are expected to have 1.6 times as many non-household contacts as Democrats, on average.

```{r}
# Model for Wave 1
contacts_R_v_D_w1 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 2))

# Model for Wave 2
contacts_R_v_D_w2 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 4))
# Model for Wave 3
contacts_R_v_D_w3 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party, data = subset(df, wave == 6))

# Define a new function to extract both the coefficient and its standard error
extract_coefficient_and_error <- function(model, coefficient_name) {
  estimate <- coef(summary(model))[coefficient_name, "Estimate"]
  std_error <- coef(summary(model))[coefficient_name, "Std. Error"]
  list(coefficient = exp(estimate), 
       lower = exp(estimate - 1.96 * std_error), 
       upper = exp(estimate + 1.96 * std_error))
}

# Extract coefficients and standard errors for each wave
coeff_wave1 <- extract_coefficient_and_error(contacts_R_v_D_w1, "political_partyRepublican")
coeff_wave2 <- extract_coefficient_and_error(contacts_R_v_D_w2, "political_partyRepublican")
coeff_wave3 <- extract_coefficient_and_error(contacts_R_v_D_w3, "political_partyRepublican")

# Combine coefficients into a data frame
coefficients_df <- data.frame(
  Wave = factor(c(1, 2, 3)),
  Coefficient = c(coeff_wave1$coefficient, coeff_wave2$coefficient, coeff_wave3$coefficient),
  Lower = c(coeff_wave1$lower, coeff_wave2$lower, coeff_wave3$lower),
  Upper = c(coeff_wave1$upper, coeff_wave2$upper, coeff_wave3$upper)
)

contacts_R_v_D_plot <- ggplot(coefficients_df, aes(x = Wave, y = Coefficient, shape = Wave)) +  # Add shape mapping to aes()
  geom_point(position = position_dodge(width = 0.25), size = 3, color = "red") +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.1, position = position_dodge(width = 0.25), color = "red") +
  scale_shape_manual(values = c(16, 15, 17),  # Define shapes for each wave
                     labels = c("Wave 1", "Wave 2", "Wave 3")) +  # Custom labels for the legend
  labs(title = "Wave-Specific Comparative Non-Household Contacts for Republicans During the Pandemic",
       subtitle = "Reference: Democrats",
       x = "Wave",
       y = "IRR",
       shape = "Wave Shapes") +  # Label for the shape legend
  theme_minimal() +
  theme(legend.position = "bottom")  # Adjust legend position

print(summary(contacts_R_v_D_w1))
print(summary(contacts_R_v_D_w2))
print(summary(contacts_R_v_D_w3))

rm(coeff_wave1,coeff_wave2,coeff_wave3,contacts_R_v_D_w1,contacts_R_v_D_w2,contacts_R_v_D_w3)
# Print the plot
print(contacts_R_v_D_plot)
```

Strange and inconcistent results with Democrats in Republican CD's
Wave 2 I don't see any difference between them and D in R CD
Wave 4 I see they're MORE likely to have non-hh contacts in R CD
Wave 6 I see they're LESS likely to have non-hh contacts in R CD

However, Republicans are pretty consitently having more non-hh contacts over time (the only clear pattern)
```{r}
contacts_DC_w2 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 2))

# Model for Wave 2
contacts_DC_w4 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 4))
# Model for Wave 3
contacts_DC_w6 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + political_party_to_CD, data = subset(df, wave == 6))

# Coefficients of interest
coeffs_of_interest <- c("political_party_to_CDDemocrat in Republican led CD",
                        "political_party_to_CDRepublican in Democratic led CD",
                        "political_party_to_CDRepublican in Republican led CD")

# Apply the function to each model
coeff_wave2 <- extract_coefficient_and_error(contacts_DC_w2, coeffs_of_interest)
coeff_wave4 <- extract_coefficient_and_error(contacts_DC_w4, coeffs_of_interest)
coeff_wave6 <- extract_coefficient_and_error(contacts_DC_w6, coeffs_of_interest)

# Add wave information to each data frame
coeff_wave2$Wave <- "Wave 1"
coeff_wave4$Wave <- "Wave 2"
coeff_wave6$Wave <- "Wave 3"

term_names_wave2 <- names(coeff_wave2$coefficient)
term_names_wave4 <- names(coeff_wave4$coefficient)
term_names_wave6 <- names(coeff_wave6$coefficient)

# Combine coefficients into a data frame
coefficients_df <- data.frame(
  Wave = factor(c(1, 1, 1, 2, 2, 2, 3, 3, 3)),
  Coefficient = c(coeff_wave2$coefficient, coeff_wave4$coefficient, coeff_wave6$coefficient),
  Lower = c(coeff_wave2$lower, coeff_wave4$lower, coeff_wave6$lower),
  Upper = c(coeff_wave2$upper, coeff_wave4$upper, coeff_wave6$upper),
  Term = c(term_names_wave2, term_names_wave4, term_names_wave6)
)

contacts_DC_plot <- ggplot(coefficients_df, aes(x = Term, y = Coefficient, color = Term, shape = Wave)) +
  geom_point(position = position_dodge(width = 0.3), size = 3) +  # Dodge applied to points
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0.1, position = position_dodge(width = 0.3)) +  # Dodge also applied to error bars
  scale_color_manual(name = "Term", 
                     values = c("blue", "purple", "red"),
                     labels = c("Dem in Rep CD", "Rep in Dem CD", "Rep in Rep CD")) +
  scale_shape_manual(values = c(16, 15, 17)) +
  theme_minimal() +
  labs(title = "Wave-Specific Comparative Non-Household Contacts for Partisans Within Congressional District Context", 
       subtitle = "Reference: Dems in Dem Districts",
       x = "Category", 
       y = "IRR") +
  scale_x_discrete(labels = c("Dems in Repub Disctricts", "Repubs in Dem Districts", "Repubs in Repub Distritics")) # Custom x-axis labels

print(contacts_DC_plot)
```
```{r}
contacts_DC_w2 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + CD_PERCENT_REPUBLICAN +political_party, data = subset(df, wave == 2))

# Model for Wave 2
contacts_DC_w4 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + as.factor(Categorical_Repub_CD_County_Share), data = subset(D_df, wave == 4))
# Model for Wave 3
contacts_DC_w6 <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_12_09 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + as.factor(Categorical_Repub_CD_County_Share), data = subset(D_df, wave == 6))
```
```{r}
print(summary(contacts_DC_w4))
print(summary(contacts_DC_w6))
```

The above is producing errors (I think because I'm subsetting to the point that some categories becomes too small). For now I'll run it across all three waves and return to the above later.

```{r}
D_nonhh_CD_per_model <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + Categorical_Repub_CD_County_Share, data = D_df)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(D_nonhh_CD_per_model)

coeffs_of_interest <- tidy_model %>%
  filter(term %in% c("Categorical_Repub_CD_County_ShareThree Quarters", 
                     "Categorical_Repub_CD_County_ShareTwo Quarters", 
                     "Categorical_Repub_CD_County_ShareLess Than a Quarter")) %>%
  mutate(
    IRR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  mutate(term = ifelse(term == "Categorical_Repub_CD_County_ShareThree Quarters", "Republican Majority", term)) %>%
  mutate(term = ifelse(term == "Categorical_Repub_CD_County_ShareTwo Quarters", "Small Democrat Majority", term)) %>%
  mutate(term = ifelse(term == "Categorical_Repub_CD_County_ShareLess Than a Quarter", "Strong Democrat Majority", term))

# Create the plot
D_nonhh_CD_per_plot <- ggplot(coeffs_of_interest, aes(x = term, y = IRR)) +
  geom_point(color = "blue", size = 3) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0, color = "blue") +
  scale_y_continuous("Incident Rate Ratio (IRR)", 
                     breaks = scales::pretty_breaks(), 
                     limits = c(NA, max(coeffs_of_interest$CI_upper) * 1.1)) +
  labs(
    title = "Incident Rate Ratios (IRR) of Non-Household Contacts by County Voter Share",
    subtitle = "Reference Category: Strong Republican Majority",
    x = "Democrats by CD Share Counties"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(D_nonhh_CD_per_plot)
print(summary(D_nonhh_CD_per_model))
```
```{r}
R_nonhh_CD_per_model <- glm.nb(num_cc_nonhh ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + Categorical_Dem_CD_County_Share, data = R_df)

# Get tidy data frame of coefficients
tidy_model <- broom::tidy(R_nonhh_CD_per_model)

coeffs_of_interest <- tidy_model %>%
  filter(term %in% c("Categorical_Dem_CD_County_ShareThree Quarters", 
                     "Categorical_Dem_CD_County_ShareTwo Quarters", 
                     "Categorical_Dem_CD_County_ShareLess Than a Quarter")) %>%
  mutate(
    IRR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  mutate(term = ifelse(term == "Categorical_Dem_CD_County_ShareThree Quarters", "Democrat Majority", term)) %>%
  mutate(term = ifelse(term == "Categorical_Dem_CD_County_ShareTwo Quarters", "Small Republican Majority", term)) %>%
  mutate(term = ifelse(term == "Categorical_Dem_CD_County_ShareLess Than a Quarter", "Strong Republican Majority", term))

# Create the plot
R_nonhh_CD_per_plot <- ggplot(coeffs_of_interest, aes(x = term, y = IRR)) +
  geom_point(color = "red", size = 3) +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0, color = "red") +
  scale_y_continuous("Incident Rate Ratio (IRR)", 
                     breaks = scales::pretty_breaks(), 
                     limits = c(NA, max(coeffs_of_interest$CI_upper) * 1.1)) +
  labs(
    title = "Incident Rate Ratios (IRR) of Non-Household Contacts by County Voter Share",
    subtitle = "Reference Category: Strong Democrat Majority",
    x = "Republicans by CD Share Counties"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(R_nonhh_CD_per_plot)
```

