---
title: "Vaccine Usage and Mask wearing"
author: "Christopher Soria"
date: "2023-12-10"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r}
library(data.table)
library(tidyverse)
library(dplyr)
library(knitr)
library(gridExtra)
library(broom)

df <- fread("/Users/chrissoria/Documents/Research/BICS_Political_Polarization/data/BICS_ZIP_Features.csv")

df$Categorical_Dem_CD_County_Share <- factor(
  df$Categorical_Dem_CD_County_Share,
  levels = c("Greater than or Equal to Three Quarters", "Three Quarters", "Two Quarters", "Less Than a Quarter"),
  ordered = FALSE
)

df$Categorical_Repub_CD_County_Share <- factor(
  df$Categorical_Repub_CD_County_Share,
  levels = c("Greater than or Equal to Three Quarters", "Three Quarters", "Two Quarters", "Less Than a Quarter"),
  ordered = FALSE
)

RD_df <- df[df$political_party %in% c("Republican", "Democrat"), ]
D_df <- df[df$political_party == "Democrat"]
R_df <- df[df$political_party == "Republican"]

D_df <- D_df[D_df$Categorical_Repub_CD_County_Share != ""]
R_df <- R_df[R_df$Categorical_Dem_CD_County_Share != ""]

names(df) <- make.unique(names(df))
names(RD_df) <- make.unique(names(RD_df))
names(D_df) <- make.unique(names(D_df))
names(R_df) <- make.unique(names(R_df))
```

Vaccination questions are only available in the 6th wave
```{r}
table(df$Vaccinated, df$wave)
```
Simple grouped average fraction of contacts carried out with a maskby vaccination status
Overall, vaccinated people are also more careful overall (wear masks more often, fewer non-hh contacts, etc)
```{r}
average_by_vaccinated <- df %>%
  group_by(Vaccinated) %>%
  summarise(
    average_num_cc_nonhh = mean(num_cc_nonhh, na.rm = TRUE),
    average_contact_reduction = mean(contact_reduction, na.rm = TRUE),
    average_concern = mean(binary_concern_strong, na.rm = TRUE),
    average_mask_usage = mean(Norm_Masks_Used, na.rm = TRUE))

print(average_by_vaccinated)
rm(average_by_vaccinated)
```
The association holds even after controls in a linear model (mortality rates, state government response, rural/urban, etc)
```{r}
vaccinated_model <- lm(Norm_Masks_Used ~  COV_County_CMR_2020_06_20 + State_Government_Response_Index_11192020 + COUNT_RUCC_CAT + resp_sex + resp_educ + resp_yob + r_working + r_race + Vaccinated, data = df)

summary(vaccinated_model)
rm(vaccinated_model)
```

